Bayesian assessment of heterogeneity in psychological phenomena

### 2023-07-04 ms.Rmd
Use R native pipe

# Save variables as numerical & factor (might need for more complex contrast/eff/etc codes)
dat <- read_csv("data/heterogeneity_dataset1_traitvalence.csv") %>% 
  # Cleaning as in Bolger et al 2019
  filter(
    response.keys == "up",
    scale(rt) < 3,
    !(id %in% c(250, 257, 272))
  ) %>% 
  # Some more cleaning
  mutate(
    person = fct_anon(factor(id)),
    trial,
    valence = factor(valenceE, levels = c(-0.5, 0.5), labels = c("Negative", "Positive")),
    rt = logrt
  ) %>% 
  select(person, trial, valence, rt) %>% 
  arrange(person, trial)
```

@@

```{r}
#| label: tab-dat1
dat %>% 
  head() %>% 
  apa_table(
    span_text_columns = FALSE, 
    digits = c(0,0,0,2),
    caption = "First six rows of example dataset 1.", 
    note = "rt is log-transformed."
  )
```

@@

```{r}
# Create a table of coefficients
tab1_lmer <- model_parameters(fit1_lmer, effects = "all") %>% 
  tibble() %>% 
  select(Parameter, Coefficient, starts_with("CI_"))

@@

tab1_brms <- parameters(fit1, centrality = "mean", effects = "all") %>% 
  tibble() %>% 
  select(Parameter, Mean, starts_with("CI_"))
```

@@

tab1_lmer %>% 
  mutate(
    across(where(is.numeric), ~number(., .01)),
    MLE = str_glue("{Coefficient} [{CI_low}, {CI_high}]"),
  ) %>% 
  select(Parameter, `Estimate [95\\%CI]` = MLE) %>% 
  mutate(
    Parameter = m1_parnames
  ) %>% 
  apa_table(
    span_text_columns = FALSE,
    caption = "Parameter estimates from Model 1.",
    escape = FALSE
  )
mu1n <- tab1_lmer[2,2,T]
mu1 <- number(mu1n, .01)
sd1n <- tab1_lmer[4,2,T]
sd1 <- number(sd1n, .01)
```

@@

p0 <- ggplot() +
  aes(xdist = dist_normal(mu1n, sd1n)) +
  scale_x_continuous(breaks = extended_breaks()) +
  coord_cartesian(xlim = c(-0.55, 0.25)) +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_text(lineheight = rel(0.5))
    ) +
  scale_fill_manual(values = c("grey90", "grey80"), na.value = "white")
d1 <- dist_normal(mu1n, sd1n) %>% 
  mean_qi(.width = c(.66, .9))

@@

post1 <- as.data.frame(fit1, variable = c("b_", "sd_", "cor_", "sigma"), regex = TRUE) %>% 
  tibble() %>% 
  rownames_to_column("Sample")
post1_sum <- fit1 %>% 
  parameters(effects = "all", centrality = "mean", dispersion = TRUE) %>% 
  tibble() %>% 
  mutate(
    Mean = number(Mean, .01), 
    SD = number(SD, .001)
  ) %>% 
  select(Parameter, Mean, SD) %>% 
  pivot_longer(c(Mean, SD), names_to = "Sample") %>%
  pivot_wider(names_from = Parameter, values_from = value)

set.seed(191)
post1 %>% 
  slice_sample(n = 6) %>% 
  arrange(as.integer(Sample)) %>% 
  mutate(
    across(-Sample, ~number(., .01))
  ) %>%
  add_row(post1_sum) %>% 
  setNames(c("Sample", m1_parnames)) %>% 
  apa_table(
    span_text_columns = FALSE,
    font_size = "small",
    midrules = 6,
    caption = "Six random samples from Model 1's parameters' posterior distributions, and their summaries.", 
    escape = FALSE,
    placement = "h"
  )
```

@@

calc_pdf <- function(posterior) {
  posterior %>% 
    crossing(x) %>% 
    mutate(
      pdf = dnorm(x, b_valence1, sd_person__valence1),
      cdf = pnorm(x, b_valence1, sd_person__valence1)
    )
}

dist_mean <- post1 %>% 
  mean_qi(b_valence1, sd_person__valence1) %>% 
  calc_pdf()

dist_samples <- post1 %>% 
  slice_sample(n = 100) %>% 
  calc_pdf()

p1 <- dist_mean %>% 
  ggplot(aes(x, pdf)) +
  scale_x_continuous(
    "Valence effect",
    expand = expansion(0),
    breaks = extended_breaks()
  ) +
  scale_y_continuous(
    "Density",
    expand = expansion(c(0.001, 0.05))
  ) +
  geom_line(
    linewidth = .6,
    col = "dodgerblue4"
  ) +
  geom_line(
    data = dist_samples,
    aes(group = Sample),
    col = "dodgerblue1",
    alpha = .33, 
    linewidth = .15
  ) +
  theme(
    axis.title.x = element_blank(), 
    plot.margin = unit(c(4,4,16,4), "pt")
  )
p2 <- distinct(dist_samples, Sample, b_valence1, sd_person__valence1) %>% 
  arrange(b_valence1) %>% 
  mutate(i = 1:n()) %>% 
  mutate(
    dist = dist_normal(b_valence1, sd_person__valence1)
  ) %>% 
  ggplot() +
  scale_x_continuous(
    "Valence effect",
    expand = expansion(0),
    breaks = extended_breaks()
  ) +
  aes(xdist = dist, y = i) +
  labs(y = "Sample") +
  stat_pointinterval(
    .width = .9,
    interval_size_range = c(.05, .1),
    alpha = .5,
    color = "dodgerblue1"
  )
(p1 / p2) &
  coord_cartesian(xlim = c(-0.55, 0.25)) &
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  ) &
  plot_layout(heights = c(75, 25)) &
  plot_annotation(tag_levels = "A")
```

@@

```{r}
p1s <- post1 %>% 
  mutate(
    hi_low = b_valence1 + qnorm(0.05) * sd_person__valence1,
    hi_high = b_valence1 + qnorm(0.95) * sd_person__valence1
  ) %>% 
  mean_qi(hi_low, hi_high) %>% 
  mutate(
    across(where(is.numeric), ~number(., .01)),
    l = str_glue("[{hi_low.lower}, {hi_low.upper}]"),
    u = str_glue("[{hi_high.lower}, {hi_high.upper}]")
  )
```

@@

p1 <- distinct(dist_samples, Sample, b_valence1, sd_person__valence1) %>%
  arrange(b_valence1) %>%
  # slice(seq(1, nrow(.), by = 2)) %>%
  mutate(i = 1:n()) %>% 
  mutate(
    dist = dist_normal(b_valence1, sd_person__valence1)
  ) %>% 
  ggplot() +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue3"), na.value = "white") +
  scale_x_continuous(
    "Valence effect",
    expand = expansion(0),
    breaks = extended_breaks()
  ) +
  scale_y_continuous(
    "Sample",
    expand = expansion(0)
  ) +
  aes(xdist = dist, y = i) +
  geom_vline(xintercept = 0, linewidth = .2, linetype = "dashed") +
  stat_slab(
    aes(fill = after_stat(x < 0)), 
    height = 15,
    slab_color = "grey10",
    slab_linewidth = .1,
    alpha = .5,
    p_limits = c(.01, .99),
    show.legend = FALSE
  )
p2 <- post1 %>% 
  mutate(
    dist = dist_normal(b_valence1, sd_person__valence1),
    pd = cdf(dist, 0),
    prope = percent(cdf(dist, 0.1) - cdf(dist, -0.1), .1)
  ) %>% 
  ggplot(aes(pd)) +
  scale_y_continuous(
    "Count",
    expand = expansion(0)
  ) +
  scale_x_continuous(
    TeX('$p^d$'),
    breaks = extended_breaks(),
    labels = ~percent(., 1)
  ) +
  stat_histinterval(
    breaks = 50,
    outline_bars = TRUE,
    slab_color = "gray10",
    slab_fill = alpha("dodgerblue1", .33),
    slab_linewidth = .2,
    justification = .01,
    point_color = "dodgerblue4", 
    interval_color = "dodgerblue4",
    .width = .90
  )
(p1 | p2) &
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) &
  plot_annotation(tag_levels = "A")
```

```{r}
tmp <- post1 %>% 
  mutate(
    dist = dist_normal(b_valence1, sd_person__valence1),
    pd = cdf(dist, 0),
    rope = cdf(dist, 0.1) - cdf(dist, -0.1),
    ratio = abs(sd_person__valence1 / b_valence1)
  ) %>% 
  mean_qi(pd, rope, ratio) %>% 
  mutate(
    pd_r = str_glue(
      "{percent(pd, .1)} [{percent(pd.lower, .1)}, {percent(pd.upper, .1)}]"
    ),
    pd_r_n = str_glue(
      "{percent(1-pd, .1)} [{percent(1-pd.upper, .1)}, {percent(1-pd.lower, .1)}]"
    ),
    rope_r = str_glue(
      "{percent(rope, .1)} [{percent(rope.lower, .1)}, {percent(rope.upper, .1)}]"
    ),
    rope_r_n = str_glue(
      "{percent(1-rope, .1)} [{percent(1-rope.upper, .1)}, {percent(1-rope.lower, .1)}]"
    ),
    ratio_r = str_glue(
      "{number(ratio, .01)} [{number(ratio.lower, .01)}, {number(ratio.upper, .01)}]"
    )
  )
```

@@

```{r}
#| label: hdist-4
#| fig.height: 2.2
#| fig.width: 4
#| fig-cap: \textbf{A}. 100 random draws from the valence effect distribution's posterior distribution. Dark area under the curve represents the proportion of effects within a region of practical equivalence to zero (ROPE) in the population for that posterior draw ($p^{ROPE}$). \textbf{B}. Histogram of all 4,000 draws from the posterior distribution of $p^{ROPE}$, and its posterior mean and 95%CI.
p1 <- distinct(dist_samples, Sample, b_valence1, sd_person__valence1) %>% 
  arrange(b_valence1) %>% 
  # slice(seq(1, nrow(.), by = 2)) %>%
  mutate(i = 1:n()) %>% 
  mutate(
    dist = dist_normal(b_valence1, sd_person__valence1)
  ) %>% 
  ggplot() +
  scale_fill_manual(
    values = c("dodgerblue1", "dodgerblue3"), 
    na.value = "white"
    ) +
  scale_x_continuous(
    "Valence effect",
    expand = expansion(0),
    breaks = extended_breaks()
  ) +
  scale_y_continuous(
    "Sample",
    expand = expansion(0)
  ) +
  aes(xdist = dist, y = i) +
  geom_vline(xintercept = 0, linewidth = .2, linetype = "dashed") +
  stat_slab(
    aes(fill = after_stat(near(x, 0, .1))), 
    height = 15,
    slab_color = "grey10",
    slab_linewidth = .1,
    alpha = .5,
    p_limits = c(.01, .99),
    show.legend = FALSE
  )
p2 <- post1 %>% 
  mutate(
    dist = dist_normal(b_valence1, sd_person__valence1),
    pd = cdf(dist, 0),
    prope = cdf(dist, 0.1) - cdf(dist, -0.1)
  ) %>% 
  ggplot(aes(prope)) +
  scale_y_continuous(
    "Count",
    expand = expansion(0)
  ) +
  scale_x_continuous(
    TeX('$p^{ROPE}$'),
    breaks = extended_breaks(),
    labels = ~percent(., 1)
  ) +
  stat_histinterval(
    breaks = 50,
    outline_bars = TRUE,
    slab_color = "gray10",
    slab_fill = alpha("dodgerblue1", .33),
    slab_linewidth = .2,
    justification = .01,
    point_color = "dodgerblue4", 
    interval_color = "dodgerblue4",
    .width = .90
  )
(p1 | p2) &
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) &
  plot_annotation(tag_levels = "A")
```

@@

```{r}
#| label: hdist-5
#| fig.height: 2.2
#| fig.width: 4
#| fig-cap: \textbf{A}. 4,000 random draws from the posterior distribution of the valence effect distribution's mean ($\beta_1$) and standard deviation ($\tau_1$). \textbf{B}. Histogram of 4,000 draws from the posterior distribution of the ratio of the valence distribution's scale over its  location $\frac{\tau_1}{\beta_1}$, and its posterior mean and 95%CI.
p1 <- post1 %>% 
  ggplot(aes(b_valence1, sd_person__valence1)) +
  scale_y_continuous(
    TeX("$\\tau_1$")
  ) +
  scale_x_continuous(
    TeX("$\\beta_1$")
  ) +
  geom_point(
    shape = 1,
    col = "dodgerblue3",
    alpha = .25,
    size = .5
  )
p2 <- post1 %>% 
  mutate(ratio = abs(sd_person__valence1 / b_valence1)) %>% 
  ggplot(aes(ratio)) +
    scale_y_continuous(
    "Count",
    expand = expansion(0)
  ) +
  scale_x_continuous(
    TeX('$\\frac{\\tau_1}{\\beta_1}$'),
    breaks = extended_breaks()
  ) +
  stat_histinterval(
    breaks = 50,
    outline_bars = TRUE,
    slab_color = "gray10",
    slab_fill = alpha("dodgerblue1", .33),
    slab_linewidth = .2,
    justification = .01,
    point_color = "dodgerblue4", 
    interval_color = "dodgerblue4",
    .width = .90
  ) +
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
  )
(p1 | p2) &
  theme(
    aspect.ratio = 1
  ) &
  plot_annotation(tag_levels = "A")
```

@@

```{r}
set.seed(999)
dat2 <- distinct(dat, person) %>% 
  mutate(
    g = sample(
      c("a", "b"), 
      length(unique(dat$person)), 
      replace = TRUE
    ),
    g = factor(g)
  ) %>% 
  right_join(dat)
contrasts(dat2$g) <- c(-0.5, 0.5)
```

@@

m2_parnames <- c(
  "$\\beta_0$", 
  "$\\beta_1$", 
  "$\\tau_0$", 
  "$\\tau_1$", 
  "$\\rho$",
  "$\\sigma$"
)
post2 <- gather_draws(fit2, `b_g.*`, `sd_.*`, `cor_.*`, `b_sigma.*`, regex = TRUE) %>% 
  ungroup() %>% 
  mutate(
    g = str_extract(.variable, "g[a|b]") %>% str_remove("g"),
    .variable = .variable %>% str_replace_all(":", "_") %>% str_remove_all("([_|:]g[a|b])+")
  )

post2 <- post2 %>% 
  pivot_wider(names_from = .variable, values_from = .value) %>% 
  mutate(
    dist = dist_normal(`b_valence1`, sd_person__valence1),
    pd = cdf(dist, 0),
    prope = cdf(dist, 0.1) - cdf(dist, -0.1),
    ratio = abs(sd_person__valence1 / `b_valence1`)
  ) %>% 
  select(-dist)

post2 %>% 
  pivot_longer(b:ratio) %>% 
  pivot_wider(names_from = g, values_from = value) %>% 
  rename(A = a, B = b) %>% 
  mutate(`B - A` = B - A) %>% 
  pivot_longer(c(A, B, `B - A`), names_to = "g") %>% 
  mutate(name = fct_inorder(name)) %>% 
  group_by(g, name) %>% 
  mean_qi(value) %>% 
  mutate(
    r = if_else(
      name %in% c("pd", "prope"),
      str_glue("{percent(value, .1)} [{number(.lower*100, .1)}, {number(.upper*100, .1)}]"),
      str_glue("{number(value, .01)} [{number(.lower, .01)}, {number(.upper, .01)}]")
      )
  ) %>% 
  mutate(
    name2 = rep(
      c(
        m2_parnames, 
        "$p^d$", 
        "$p^{ROPE}$", 
        "$\\frac{\\tau_1}{\\beta_1}$"
        ), 
      times = 3
    )
  ) %>% 
  select(Parameter = name2, g, r) %>% 
  mutate(g = str_glue("Group {toupper(g)}")) %>% 
  pivot_wider(names_from = g, values_from = r) %>% 
  apa_table(
    span_text_columns = FALSE,
    font_size = "scriptsize",
    caption = "Parameter estimates from Model 2.",
    escape = FALSE
  )
```

>>>>

# Save variables as numerical & factor (might need for more complex contrast/eff/etc codes)
dat <- read_csv("data/heterogeneity_dataset1_traitvalence.csv") |> 
  # Cleaning as in Bolger et al 2019
  filter(
    response.keys == "up",
    scale(rt) < 3,
    !(id %in% c(250, 257, 272))
  ) |> 
  # Some more cleaning
  mutate(
    person = fct_anon(factor(id)),
    trial,
    valence = factor(valenceE, levels = c(-0.5, 0.5), labels = c("Negative", "Positive")),
    rt = logrt
  ) |> 
  select(person, trial, valence, rt) |> 
  arrange(person, trial)
```

@@

```{r}
#| label: tab-dat1
dat |> 
  head() |> 
  apa_table(
    span_text_columns = FALSE, 
    digits = c(0,0,0,2),
    caption = "First six rows of example dataset 1.", 
    note = "rt is log-transformed."
  )
```

@@

```{r}
# Create a table of coefficients
tab1_lmer <- model_parameters(fit1_lmer, effects = "all") |> 
  tibble() |> 
  select(Parameter, Coefficient, starts_with("CI_"))

@@

tab1_brms <- parameters(fit1, centrality = "mean", effects = "all") |> 
  tibble() |> 
  select(Parameter, Mean, starts_with("CI_"))
```

@@

tab1_lmer |> 
  mutate(
    across(where(is.numeric), ~number(., .01)),
    MLE = str_glue("{Coefficient} [{CI_low}, {CI_high}]"),
  ) |> 
  select(Parameter, `Estimate [95\\%CI]` = MLE) |> 
  mutate(
    Parameter = m1_parnames
  ) |> 
  apa_table(
    span_text_columns = FALSE,
    caption = "Parameter estimates from Model 1.",
    escape = FALSE
  )
mu1n <- tab1_lmer[2,2,T]
mu1 <- number(mu1n, .01)
sd1n <- tab1_lmer[4,2,T]
sd1 <- number(sd1n, .01)
```

@@

p0 <- ggplot() +
  aes(xdist = dist_normal(mu1n, sd1n)) +
  scale_x_continuous(breaks = extended_breaks()) +
  coord_cartesian(xlim = c(-0.55, 0.25)) +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_text(lineheight = rel(0.5))
    ) +
  scale_fill_manual(values = c("grey90", "grey80"), na.value = "white")
d1 <- dist_normal(mu1n, sd1n) |> 
  mean_qi(.width = c(.66, .9))

@@

post1 <- as.data.frame(fit1, variable = c("b_", "sd_", "cor_", "sigma"), regex = TRUE) |> 
  tibble() |> 
  rownames_to_column("Sample")
post1_sum <- fit1 |> 
  parameters(effects = "all", centrality = "mean", dispersion = TRUE) |> 
  tibble() |> 
  mutate(
    Mean = number(Mean, .01), 
    SD = number(SD, .001)
  ) |> 
  select(Parameter, Mean, SD) |> 
  pivot_longer(c(Mean, SD), names_to = "Sample") |>
  pivot_wider(names_from = Parameter, values_from = value)

set.seed(191)
post1 |> 
  slice_sample(n = 6) |> 
  arrange(as.integer(Sample)) |> 
  mutate(
    across(-Sample, ~number(., .01))
  ) |>
  add_row(post1_sum) |> 
  setNames(c("Sample", m1_parnames)) |> 
  apa_table(
    span_text_columns = FALSE,
    font_size = "small",
    midrules = 6,
    caption = "Six random samples from Model 1's parameters' posterior distributions, and their summaries.", 
    escape = FALSE,
    placement = "h"
  )
```

@@

calc_pdf <- function(posterior) {
  posterior |> 
    crossing(x) |> 
    mutate(
      pdf = dnorm(x, b_valence1, sd_person__valence1),
      cdf = pnorm(x, b_valence1, sd_person__valence1)
    )
}

dist_mean <- post1 |> 
  mean_qi(b_valence1, sd_person__valence1) |> 
  calc_pdf()

dist_samples <- post1 |> 
  slice_sample(n = 100) |> 
  calc_pdf()

p1 <- dist_mean |> 
  ggplot(aes(x, pdf)) +
  scale_x_continuous(
    "Valence effect",
    expand = expansion(0),
    breaks = extended_breaks()
  ) +
  scale_y_continuous(
    "Density",
    expand = expansion(c(0.001, 0.05))
  ) +
  geom_line(
    linewidth = .6,
    col = "dodgerblue4"
  ) +
  geom_line(
    data = dist_samples,
    aes(group = Sample),
    col = "dodgerblue1",
    alpha = .33, 
    linewidth = .15
  ) +
  theme(
    axis.title.x = element_blank(), 
    plot.margin = unit(c(4,4,16,4), "pt")
  )
p2 <- distinct(dist_samples, Sample, b_valence1, sd_person__valence1) |> 
  arrange(b_valence1) |> 
  mutate(i = 1:n()) |> 
  mutate(
    dist = dist_normal(b_valence1, sd_person__valence1)
  ) |> 
  ggplot() +
  scale_x_continuous(
    "Valence effect",
    expand = expansion(0),
    breaks = extended_breaks()
  ) +
  aes(xdist = dist, y = i) +
  labs(y = "Sample") +
  stat_pointinterval(
    .width = .9,
    interval_size_range = c(.05, .1),
    alpha = .5,
    color = "dodgerblue1"
  )
(p1 / p2) &
  coord_cartesian(xlim = c(-0.55, 0.25)) &
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  ) &
  plot_layout(heights = c(75, 25)) &
  plot_annotation(tag_levels = "A")
```

@@

```{r}
p1s <- post1 |> 
  mutate(
    hi_low = b_valence1 + qnorm(0.05) * sd_person__valence1,
    hi_high = b_valence1 + qnorm(0.95) * sd_person__valence1
  ) |> 
  mean_qi(hi_low, hi_high) |> 
  mutate(
    across(where(is.numeric), ~number(., .01)),
    l = str_glue("[{hi_low.lower}, {hi_low.upper}]"),
    u = str_glue("[{hi_high.lower}, {hi_high.upper}]")
  )
```

@@

p1 <- distinct(dist_samples, Sample, b_valence1, sd_person__valence1) |>
  arrange(b_valence1) |>
  # slice(seq(1, nrow(.), by = 2)) |>
  mutate(i = 1:n()) |> 
  mutate(
    dist = dist_normal(b_valence1, sd_person__valence1)
  ) |> 
  ggplot() +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue3"), na.value = "white") +
  scale_x_continuous(
    "Valence effect",
    expand = expansion(0),
    breaks = extended_breaks()
  ) +
  scale_y_continuous(
    "Sample",
    expand = expansion(0)
  ) +
  aes(xdist = dist, y = i) +
  geom_vline(xintercept = 0, linewidth = .2, linetype = "dashed") +
  stat_slab(
    aes(fill = after_stat(x < 0)), 
    height = 15,
    slab_color = "grey10",
    slab_linewidth = .1,
    alpha = .5,
    p_limits = c(.01, .99),
    show.legend = FALSE
  )
p2 <- post1 |> 
  mutate(
    dist = dist_normal(b_valence1, sd_person__valence1),
    pd = cdf(dist, 0),
    prope = percent(cdf(dist, 0.1) - cdf(dist, -0.1), .1)
  ) |> 
  ggplot(aes(pd)) +
  scale_y_continuous(
    "Count",
    expand = expansion(0)
  ) +
  scale_x_continuous(
    TeX('$p^d$'),
    breaks = extended_breaks(),
    labels = ~percent(., 1)
  ) +
  stat_histinterval(
    breaks = 50,
    outline_bars = TRUE,
    slab_color = "gray10",
    slab_fill = alpha("dodgerblue1", .33),
    slab_linewidth = .2,
    justification = .01,
    point_color = "dodgerblue4", 
    interval_color = "dodgerblue4",
    .width = .90
  )
(p1 | p2) &
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) &
  plot_annotation(tag_levels = "A")
```

```{r}
tmp <- post1 |> 
  mutate(
    dist = dist_normal(b_valence1, sd_person__valence1),
    pd = cdf(dist, 0),
    rope = cdf(dist, 0.1) - cdf(dist, -0.1),
    ratio = abs(sd_person__valence1 / b_valence1)
  ) |> 
  mean_qi(pd, rope, ratio) |> 
  mutate(
    pd_r = str_glue(
      "{percent(pd, .1)} [{percent(pd.lower, .1)}, {percent(pd.upper, .1)}]"
    ),
    pd_r_n = str_glue(
      "{percent(1-pd, .1)} [{percent(1-pd.upper, .1)}, {percent(1-pd.lower, .1)}]"
    ),
    rope_r = str_glue(
      "{percent(rope, .1)} [{percent(rope.lower, .1)}, {percent(rope.upper, .1)}]"
    ),
    rope_r_n = str_glue(
      "{percent(1-rope, .1)} [{percent(1-rope.upper, .1)}, {percent(1-rope.lower, .1)}]"
    ),
    ratio_r = str_glue(
      "{number(ratio, .01)} [{number(ratio.lower, .01)}, {number(ratio.upper, .01)}]"
    )
  )
```

@@

```{r}
#| label: hdist-4
#| fig.height: 2.2
#| fig.width: 4
#| fig-cap: \textbf{A}. 100 random draws from the valence effect distribution's posterior distribution. Dark area under the curve represents the proportion of effects within a region of practical equivalence to zero (ROPE) in the population for that posterior draw ($p^{ROPE}$). \textbf{B}. Histogram of all 4,000 draws from the posterior distribution of $p^{ROPE}$, and its posterior mean and 95%CI.
p1 <- distinct(dist_samples, Sample, b_valence1, sd_person__valence1) |> 
  arrange(b_valence1) |> 
  # slice(seq(1, nrow(.), by = 2)) |>
  mutate(i = 1:n()) |> 
  mutate(
    dist = dist_normal(b_valence1, sd_person__valence1)
  ) |> 
  ggplot() +
  scale_fill_manual(
    values = c("dodgerblue1", "dodgerblue3"), 
    na.value = "white"
    ) +
  scale_x_continuous(
    "Valence effect",
    expand = expansion(0),
    breaks = extended_breaks()
  ) +
  scale_y_continuous(
    "Sample",
    expand = expansion(0)
  ) +
  aes(xdist = dist, y = i) +
  geom_vline(xintercept = 0, linewidth = .2, linetype = "dashed") +
  stat_slab(
    aes(fill = after_stat(near(x, 0, .1))), 
    height = 15,
    slab_color = "grey10",
    slab_linewidth = .1,
    alpha = .5,
    p_limits = c(.01, .99),
    show.legend = FALSE
  )
p2 <- post1 |> 
  mutate(
    dist = dist_normal(b_valence1, sd_person__valence1),
    pd = cdf(dist, 0),
    prope = cdf(dist, 0.1) - cdf(dist, -0.1)
  ) |> 
  ggplot(aes(prope)) +
  scale_y_continuous(
    "Count",
    expand = expansion(0)
  ) +
  scale_x_continuous(
    TeX('$p^{ROPE}$'),
    breaks = extended_breaks(),
    labels = ~percent(., 1)
  ) +
  stat_histinterval(
    breaks = 50,
    outline_bars = TRUE,
    slab_color = "gray10",
    slab_fill = alpha("dodgerblue1", .33),
    slab_linewidth = .2,
    justification = .01,
    point_color = "dodgerblue4", 
    interval_color = "dodgerblue4",
    .width = .90
  )
(p1 | p2) &
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  ) &
  plot_annotation(tag_levels = "A")
```

@@

```{r}
#| label: hdist-5
#| fig.height: 2.2
#| fig.width: 4
#| fig-cap: \textbf{A}. 4,000 random draws from the posterior distribution of the valence effect distribution's mean ($\beta_1$) and standard deviation ($\tau_1$). \textbf{B}. Histogram of 4,000 draws from the posterior distribution of the ratio of the valence distribution's scale over its  location $\frac{\tau_1}{\beta_1}$, and its posterior mean and 95%CI.
p1 <- post1 |> 
  ggplot(aes(b_valence1, sd_person__valence1)) +
  scale_y_continuous(
    TeX("$\\tau_1$")
  ) +
  scale_x_continuous(
    TeX("$\\beta_1$")
  ) +
  geom_point(
    shape = 1,
    col = "dodgerblue3",
    alpha = .25,
    size = .5
  )
p2 <- post1 |> 
  mutate(ratio = abs(sd_person__valence1 / b_valence1)) |> 
  ggplot(aes(ratio)) +
    scale_y_continuous(
    "Count",
    expand = expansion(0)
  ) +
  scale_x_continuous(
    TeX('$\\frac{\\tau_1}{\\beta_1}$'),
    breaks = extended_breaks()
  ) +
  stat_histinterval(
    breaks = 50,
    outline_bars = TRUE,
    slab_color = "gray10",
    slab_fill = alpha("dodgerblue1", .33),
    slab_linewidth = .2,
    justification = .01,
    point_color = "dodgerblue4", 
    interval_color = "dodgerblue4",
    .width = .90
  ) +
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
  )
(p1 | p2) &
  theme(
    aspect.ratio = 1
  ) &
  plot_annotation(tag_levels = "A")
```

@@

```{r}
set.seed(999)
dat2 <- distinct(dat, person) |> 
  mutate(
    g = sample(
      c("a", "b"), 
      length(unique(dat$person)), 
      replace = TRUE
    ),
    g = factor(g)
  ) |> 
  right_join(dat)
contrasts(dat2$g) <- c(-0.5, 0.5)
```

@@

m2_parnames <- c(
  "$\\beta_0$", 
  "$\\beta_1$", 
  "$\\tau_0$", 
  "$\\tau_1$", 
  "$\\rho$",
  "$\\sigma$"
)
post2 <- gather_draws(fit2, `b_g.*`, `sd_.*`, `cor_.*`, `b_sigma.*`, regex = TRUE) |> 
  ungroup() |> 
  mutate(
    g = str_extract(.variable, "g[a|b]") |> str_remove("g"),
    .variable = .variable |> str_replace_all(":", "_") |> str_remove_all("([_|:]g[a|b])+")
  )

post2 <- post2 |> 
  pivot_wider(names_from = .variable, values_from = .value) |> 
  mutate(
    dist = dist_normal(`b_valence1`, sd_person__valence1),
    pd = cdf(dist, 0),
    prope = cdf(dist, 0.1) - cdf(dist, -0.1),
    ratio = abs(sd_person__valence1 / `b_valence1`)
  ) |> 
  select(-dist)

post2 |> 
  pivot_longer(b:ratio) |> 
  pivot_wider(names_from = g, values_from = value) |> 
  rename(A = a, B = b) |> 
  mutate(`B - A` = B - A) |> 
  pivot_longer(c(A, B, `B - A`), names_to = "g") |> 
  mutate(name = fct_inorder(name)) |> 
  group_by(g, name) |> 
  mean_qi(value) |> 
  mutate(
    r = if_else(
      name %in% c("pd", "prope"),
      str_glue("{percent(value, .1)} [{number(.lower*100, .1)}, {number(.upper*100, .1)}]"),
      str_glue("{number(value, .01)} [{number(.lower, .01)}, {number(.upper, .01)}]")
      )
  ) |> 
  mutate(
    name2 = rep(
      c(
        m2_parnames, 
        "$p^d$", 
        "$p^{ROPE}$", 
        "$\\frac{\\tau_1}{\\beta_1}$"
        ), 
      times = 3
    )
  ) |> 
  select(Parameter = name2, g, r) |> 
  mutate(g = str_glue("Group {toupper(g)}")) |> 
  pivot_wider(names_from = g, values_from = r) |> 
  apa_table(
    span_text_columns = FALSE,
    font_size = "scriptsize",
    caption = "Parameter estimates from Model 2.",
    escape = FALSE
  )
```
